Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-06-25 WSSSPE2_report/WSSSPE2_review.tex
removing extra author info
Expand ICT abbreviation

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$,
\\Colin C. Venters$^{(5)}$, James Howison$^{(6)}$, Frank Seinstra$^{(7)}$, Matthew Jones$^{(8)}$
\\Karen Cranston$^{(9)}$, Thomas L. Clune$^{(10)}$, Miguel de Val-Borro$^{(11)}$, Richard Littauer$^{(12)}$,
\\more TBD by contributions}
%\author{Gabrielle Allen$^{(11)}$,  \\
%$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{dsk@uchicago.edu}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA; \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK; \url{N.ChueHong@software.ac.uk}}
%
\thanks{{}$^{(5)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
\thanks{{}$^{(6)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(7)}$ Netherlands eScience Centre, Amsterdam, Netherlands \url{F.Seinstra@esciencecenter.nl}}
%
\thanks{{}$^{(8)}$ National Center for Ecological Analysis and Synthesis, Santa Barbara, CA, USA; \url{jones@nceas.ucsb.edu}}
%
\thanks{{}$^{(9)}$ National Evolutionary Synthesis Center, Durham, NC, USA; \url{karen.cranston@nescent.org}}
%
\thanks{{}$^{(10)}$ NASA Goddard Space Flight Center, Greenbelt, MD, USA; \url{Thomas.L.Clune@nasa.gov}}
%
\thanks{{}$^{(11)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; \url{mdevalbo@astro.princeton.edu}}
%
\thanks{{}$^{(12)}$ MIT, Boston, MA, USA \& University of Saarland, Germany \url{richard.littauer@gmail.com}}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}

@@

At the start of the discussion, the breakout group brought forth the important
observation of the wide disparity in commonly accepted habits of publication in
different research fields. In domains which have, historically, relied on large
groups of researchers collaborating towards a common goal (e.g., high-energy
physics, astronomy), publications often have tens or even hundreds of co-authors
(with some papers in experimental particle physics having over 3000.) In other
domains, the number of co-authors is typically much smaller, with, in some
cases, even a preference for single-author papers. Similarly, the various
platforms for publication are valued differently in different domains. Most
commonly, publications in peer-reviewed scientific journals are regarded as the
most important and most impactful. However, in certain domains, especially in
Computer Science, many researchers typically regard conference proceedings as
their prime publication target. It is often suggested that this difference is
due to the rapid developments in ICT science, a pace that can not be upheld by
traditional peer-reviewed journals. Whatever the causes, any useful taxonomy of
contributorship or guideline for tenure review should take such differences into
account.

>>>>

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$,
\\Colin C. Venters$^{(5)}$, James Howison$^{(6)}$, Frank Seinstra$^{(7)}$, Matthew Jones$^{(8)}$
\\Karen Cranston$^{(9)}$, Thomas L. Clune$^{(10)}$, Miguel de Val-Borro$^{(11)}$, Richard Littauer$^{(12)}$}
%\author{Gabrielle Allen$^{(11)}$,  \\
%$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{dsk@uchicago.edu}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA; \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK; \url{N.ChueHong@software.ac.uk}}
%
\thanks{{}$^{(5)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
\thanks{{}$^{(6)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(7)}$ Netherlands eScience Centre, Amsterdam, Netherlands \url{F.Seinstra@esciencecenter.nl}}
%
\thanks{{}$^{(8)}$ National Center for Ecological Analysis and Synthesis, Santa Barbara, CA, USA; \url{jones@nceas.ucsb.edu}}
%
\thanks{{}$^{(9)}$ National Evolutionary Synthesis Center, Durham, NC, USA; \url{karen.cranston@nescent.org}}
%
\thanks{{}$^{(10)}$ NASA Goddard Space Flight Center, Greenbelt, MD, USA; \url{Thomas.L.Clune@nasa.gov}}
%
\thanks{{}$^{(11)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; \url{mdevalbo@astro.princeton.edu}}
%
\thanks{{}$^{(12)}$ MIT, Boston, MA, USA \& University of Saarland, Germany \url{richard.littauer@gmail.com}}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}

@@

At the start of the discussion, the breakout group brought forth the important
observation of the wide disparity in commonly accepted habits of publication in
different research fields. In domains which have, historically, relied on large
groups of researchers collaborating towards a common goal (e.g., high-energy
physics, astronomy), publications often have tens or even hundreds of co-authors
(with some papers in experimental particle physics having over 3000.) In other
domains, the number of co-authors is typically much smaller, with, in some
cases, even a preference for single-author papers. Similarly, the various
platforms for publication are valued differently in different domains. Most
commonly, publications in peer-reviewed scientific journals are regarded as the
most important and most impactful. However, in certain domains, especially in
Computer Science, many researchers typically regard conference proceedings as
their prime publication target. It is often suggested that this difference is
due to the rapid developments in information technology, a pace that can not be upheld by
traditional peer-reviewed journals. Whatever the causes, any useful taxonomy of
contributorship or guideline for tenure review should take such differences into
account.
